### 2024-02-13 documentation/thesis/thesis_document.tex
build

@@

As the following, the motivation for the development of this framework
is listed. A brief introduction to the topic of low-field \gls{mri} is
given, followed by the research problem to be solved by this work.

@@

@@

The teslameter is connected to the microcontroller using two free
\gls{gpio}s in \gls{uart} mode. The firmware was adapted using a
separate build configuration. In order to be able to read and correctly
interpret the data from the microcontoller, the serial protocol from
table \ref{Voltcraft_GM70_serial_protocol.csv} of the sensor was
implemented in a customized version of the
\passthrough{\lstinline!CustomSensor!} class
\ref{lst:CustomSensorClass}.

@@

\begin{longtable}[]{@{}lll@{}}
\caption{Voltcraft GM70 serial protocol
\label{Voltcraft_GM70_serial_protocol.csv}}\tabularnewline
\toprule
BYTE-INDEX & REPRESENTATION & VALUE\tabularnewline
\midrule
\endfirsthead
\toprule
BYTE-INDEX & REPRESENTATION & VALUE\tabularnewline
\midrule
\endhead
0 & PREAMBLE & 0x2\tabularnewline
1 & & 0x1\tabularnewline
2 & & 0x4\tabularnewline
3 & UNIT & `B' =\textgreater{} Gauss `E' =\textgreater{}
mT\tabularnewline
5 & POLARITY & `1' =\textgreater{} \emph{0.1 `2' =\textgreater{}
}0.01\tabularnewline
6 & value MSB & 0x-0xFF\tabularnewline
13 & value LSB & 0x-0xFF\tabularnewline
14 & STOP & 0x3\tabularnewline
\bottomrule
\end{longtable}

>>>>

As the following, the motivation for the development of this framework
is listed. The chapter provides a brief introduction into the problem
domain, delineates the scope and boundaries of the present research,
surveys the current state of the art in low-field MRI research and
applications, articulates the research question driving this thesis and
delineates the anticipated use cases and benefits that will be explored
and analyzed throughout the study.

@@

Magnetic Resonance Imaging \gls{mri} stands as a cornerstone in clinical
diagnostics, utilizing the principles of nuclear magnetic resonance
\gls{nmr} to generate cross-sectional black-and-white images of the
body. This indispensable method plays a crucial role in contemporary
medicine and research, contributing significantly to saving lives.
Despite its widespread use, traditional MRI systems often rely on large,
heavy, and expensive magnets to achieve the necessary homogeneity of the
magnetic field for accurate imaging. \cite{Nitz2016}

Various types of magnets find application in different \gls{mri}
systems. Permanent magnets generate a steady yet relatively weak
magnetic field, electro magnets are energized by electrical currents,
and superconducting electro magnets produce magnetic fields through
electricity and induction. Regardless of the type, the primary objective
is to create a homogeneous magnetic field within the \gls{mri}. The
higher the homogeneity, the more accurate the measurements. This uniform
magnetic field aligns the molecules within the body or object, setting
the stage for a second magnetic system to stimulate these molecules for
measurements.

The challenge with conventional first-order homogeneity systems lies in
their substantial size, weight, and cost. Even when targeting smaller
areas of the body, large devices are often necessary. In response to
this, there is a growing interest in developing low-field \gls{mri}
systems that utilize various magnet types, including permanent magnets.
These systems, while offering advantages in energy efficiency and
reduced complexity, face a significant challenge related to the inherent
variability in the strength of permanent magnets. Achieving homogeneity
in the magnetic field is crucial for accurate imaging or comparative
analyses. While incapable of producing images due to lower magnetic
field strength, low-field systems facilitate the comparison of different
field behaviors and the identification of anomalies. O'Reilly and
Teeuwisse and de Gans \cite{OReilly2019-rn} have already
demonstrated low-cost and small-scale implementations with low-field
\gls{mri} in 2021.

Permanent magnets, usually arranged in a circular ``Hallbach array''
around the \gls{mri}, are commonly employed in low-field systems.
However, their drawback is the inherent variability in strength,
complicating the achievement of a homogeneous field and requiring
precise strength information for correct magnet ordering and \gls{mri}
construction.

The focus of this thesis is on advancing low-frequency \gls{mri}
technology by addressing the sensor-usability of permanent magnets used
in these systems. The variability in the strength of permanent magnets
poses a significant obstacle to constructing an \gls{mri} with the
necessary precision for homogenous field generation.

To address this challenge, the thesis proposes the development of a
comprehensive hardware and software framework. The hardware system aims
to selectively measure magnetic fields at different locations or fully
around a permanent magnet using different sensors. The accompanying
open-source software is designed not only to facilitate measurements
with different sensors but also to enable the characterization of
different objects.

The sensor testing process involves two key tests. Firstly, the
linearity of the magnetic fields is measured with all sensors to assess
the feasibility of using specific sensors. Secondly, the homogeneity of
the sensors is evaluated to determine its capability to measure with
precision greater than 1,000 \gls{ppm}.

This research initiative seeks to contribute to the improvement of
low-frequency \gls{mri} systems by enhancing the accuracy of permanent
magnet characterization. The outcomes of this thesis will provide
insights into the selection and evaluation of sensors for future
low-field \gls{mri} research, ultimately contributing to advancements in
medical imaging technologies.

@@

Contemporary most MRI machines employ high-field superconducting magnets
cooled cryogenically, delivering exceptional image resolution. However,
the associated costs, space requirements, and safety considerations can
be substantial. In contrast, permanent magnets present an economical and
space-efficient alternative. Nevertheless, they generate lower magnetic
field strengths, impacting the signal-to-noise ratio (SNR) and resulting
in lower image resolution within clinically viable scan times.
\cite{Arnold2023-cn}

In response to these challenges, recent endeavors in both academia and
industry aim to leverage the benefits of lower field strength---such as
reduced costs, a smaller device footprint, and diminished safety
concerns---while addressing the inherent drawbacks that compromise image
quality (refer to Table 1). The optimization of low-field approaches is
becoming increasingly prevalent, tailored to specific clinical inquiries
and contexts.

To overcome limitations associated with lower field strengths, ongoing
research focuses on the meticulous selection and validation of use
cases. This strategic approach is essential for ensuring that the
advantages of lower cost and reduced device size are harnessed without
sacrificing diagnostic accuracy or compromising patient outcomes.
\cite{Arnold2023-cn}

@@

The teslameter is connected to the microcontroller using two free
\gls{gpio}s in \gls{uart} mode. The firmware was adapted using a
separate build configuration. In order to be able to read and correctly
interpret the data from the microcontoller, the serial protocol of the
sensor was implemented in a customized version of the
\passthrough{\lstinline!CustomSensor!} class
\ref{lst:CustomSensorClass}.

@@
